Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-07-13 paper.tex
Reword clean MIDI subset description

For evaluation, we need a collection of MIDI-audio pairs which are correctly matched.
Our approach can then be judged based on how accurately it is able to recover these pairings using the content of the audio and MIDI files alone.
We identified a subset of files where the directory name indicated the artist and the filename gave the song title.
With some additional cleaning, we were able to match this metadata against the Million Song Dataset to obtain a ground-truth set of matched MIDI-audio pairs which we call the ``clean MIDI subset''.

To develop our cross-modality hashing scheme, we further require a collection of {\em aligned} MIDI and audio files, to supply the matching pairs of feature vectors from each domain that will be used to train our model for hashing MIDI and audio features to a common Hamming space (described in Section \ref{sec:hashing}).
Given matched audio and MIDI files, we can use existing alignment techniques to create these alignments, but we must additionally ensure that the alignments are successful.
Even at the scale of this reduced set of training data, manual alignment verification is impractical, so we developed an improved quality score which we describe in Section \ref{sec:score}.

@@

We first extracted the song title and artist from each entry in the clean MIDI subset based on file and directory name.
The resulting metadata needs additional canonicalization; for example, ``The Beatles'' ``Beatles, The'', ``Beatles'', and ``The Beatles John Paul Ringo George'' all appear as artists.
To normalize these issues, we applied some manual text processing and resolved the artists and song titles against the Freebase \cite{bollacker2008freebase} and Echo Nest\footnote{\texttt{http://developer.echonest.com/docs/v4}} databases.
This resulted in 17,243 MIDI files for 10,060 unique songs.

>>>>

For evaluation, we need a collection of ground-truth MIDI-audio pairs which are correctly matched.
Our approach can then be judged based on how accurately it is able to recover these pairings using the content of the audio and MIDI files alone.
To develop our cross-modality hashing scheme, we further require a collection of {\em aligned} MIDI and audio files, to supply the matching pairs of feature vectors from each domain that will be used to train our model for hashing MIDI and audio features to a common Hamming space (described in Section \ref{sec:hashing}).
Given matched audio and MIDI files, existing alignment techniques can be used to create this training data; however, we must exclude incorrect matches and failed alignments.
Even at the scale of this reduced set of training data, manual alignment verification is impractical, so we developed an improved alignment quality score which we describe in Section \ref{sec:score}.

@@

To obtain a collection of MIDI-audio pairs, we first separated a subset of MIDI files for which the directory name corresponded to the song's artist and the filename gave the song's title.
The resulting metadata needed additional canonicalization; for example, ``The Beatles'' ``Beatles, The'', ``Beatles'', and ``The Beatles John Paul Ringo George'' all appeared as artists.
To normalize these issues, we applied some manual text processing and resolved the artists and song titles against the Freebase \cite{bollacker2008freebase} and Echo Nest\footnote{\texttt{http://developer.echonest.com/docs/v4}} databases.
This resulted in a collection of 17,243 MIDI files for 10,060 unique songs, which we will refer to as the ``clean MIDI subset''..
